%\newpage
\section{Experiment Introduction Letter}

\textbf{Project Title} \\
Evaluation of electrotactile feedback schemes in combination with myoelectric prosthetic control - closing the loop. 

\textbf{Experiment Purpose} \\
When a person gets amputated on the lower arm, he/she can receive a functional prosthesis. This is controlled by muscle signals from the user, where the muscle signals are translated into a prosthesis movement. However, many functional prostheses do not provide sensory feedback, which results in some users to abandon their prosthesis. \\
The purpose of the experiment is to compare how subjects perform in an evaluation test when receiving feedback from two different electrical stimulation configurations, while controlling a virtual prosthesis. The results might provide information on which feedback that seems more intuitive to use in a real prosthesis.   

\textbf{Experiment Overview} \\
The experiment will take place in the laboratory $D3-107$ at Aalborg University. The duration of the experiment is estimated to be 2 hours and 30 minutes. During the experiment a myoelectric armband will be placed on the dominant forearm and will be used to record muscle activity during the performance of four different hand gestures. Subsequently, a test of the ability to reproduce the gestures will be made. \\
Afterwards, an electrode armband, capable of delivering electrical stimulation at 16 different locations will be placed on the non-dominant arm. A test to determine the electrical perception and tolerance level for the subject will then be carried out. The subject will then be made familiar and trained in understanding two different feedback configurations representing possible states which the virtual prosthesis might produce. A test of the subjects ability understand the feedback while making the trained hand gestures will be made right after familiarization and training for each feedback configuration. \\
On the day of the experiment please refrain from using any types of sensory deprivation drugs (painkillers and the likes). The test subject will not receive monetary reimbursement upon completing the experiment.  