\section{Closing the Loop}

The loss of a limb does not only result in loss of motor function as sensory function also gets impaired. Providing an amputee with a prosthetic device, which does not provide sensory feedback, only restores one half of the once closed motor/sensory loop. To close the loop the prosthetic device needs to extract proprioceptive and exteroceptive information, which should be conveyed to the amputee in a intuitive and meaningful way \cite{Markovic2018}. This can be achieved using methods of sensory substitution as mentioned in \secref{senssub}. 

Closing the loop is a well recognized need amongst prosthetic users and using substitutional sensory feedback holds the possibility of lowering need for visual attention to track correct prosthetic movement. This might furthermore improve easiness of use and embodiment, which could lower rejection rates. \cite{Strbac2016} However, the advantages of closing the loop by providing sensory substitution feedback have been contradictory \cite{Jorgovanovic2014}. In 2008, Cipriani et al. \cite{Cipriani2008} investigated the use of vibroctacile feedback for improving prosthesis grasp function and did not find any improvement when providing the sensory feedback. Later findings by Witteveen et al. \cite{Witteveen2012} disproved this as they found that when providing information of grasp force and slip through vibrotactile feedback improved a virtual grasping task. 

Even though studies like \cite{Jorgovanovic2014,Witteveen2012} found closing the loop by providing grasp force sensory feedback helpful, currently only one commercial feedback providing device, VINCENT evolution 2 (Vincent Systems Gmbh, DE), is available \cite{Systems2005}. However, no devices have yet to implement means of proprioceptive feedback. Additionally, closed-loop control systems bypassing human interaction have also been investigated and implemented by commercial manufacturers i.e. Otto Bock and RSL steeper. Actuators are made to autonomously adjust grip force based on sensors located in the prosthetic hand, thereby not involving the user in the final execution of the task. \cite{Xu2016} Such an approach might improve reliability of the prosthesis, but does not provide proprioceptive and exteroceptive feedback to the user, hence not promoting full naturalness.  




